An introduction to Docker for reproducible research, with examples from the R environment

### 2014-09-19 docker-paper/manuscript.Rmd
more minor edits

That will take a while to download the image the first time you run
it. A boot2docker user will then need to determine the ip address assigned
to boot2docker, while a Linux user can just specify `http://localhost`:

@@

This acts like a software dependency; but unlike other software, a
Dockerfile must have exactly one dependency (one `FROM` line). Note that
a particular version of the dependency can be specified using the `:`.
One can in fact be much more precise, declaring not only version numbers
like `ubuntu:14:04`, but specific cryptographic hashes that ensure we
get the exact same image every time.

@@

Using Docker containers to distribute reproducible research should be
seen as an approach that is synergistic with, rather than an alternative
to, other technical tools for ensuring computational reproducibility.
Existing tools for managing dependencies for a particular language [R
packages, Ruby gems, etc, see @Ooms_2014] can easily be employed within a
Docker-based approach, allowing the operating-systems level virtualization
to sidestep potential issues such as external library dependencies or
conflicts with existing user libraries.  Other approaches that facilitate
reproducible research also introduce additional software dependencies
and possible points of failure [@FitzJohn_2014]. One example includes
dynamic documents [_e.g._ @Leisch_2002; @Peng_2011; @Xie_2013] which embed
the code required to re-generate the results within the manuscript.  As a
result, it is necessary to package the appropriate typesetting libaries
(_e.g._ \LaTeX) along with the code libaries such that the document executes
successfully for different researchers and platforms.

@@

>>>>

That will take a while to download the image the first time you run it. A
boot2docker user will then need to determine the ip address assigned
to boot2docker as shown below, while a Linux user can just specify
`http://localhost`.

@@

This acts like a software dependency; but unlike other software, a
Dockerfile must have exactly one dependency (one `FROM` line). Note that
a particular version of the dependency can be specified using the `:` notation.
One can in fact be much more precise, declaring not only version numbers
like `ubuntu:14:04`, but specific cryptographic hashes that ensure we
get the exact same image every time.

@@

Using Docker containers to distribute reproducible research should be
seen as an approach that is synergistic with, rather than an alternative
to, other technical tools for ensuring computational reproducibility.
Existing tools for managing dependencies for a particular language [_e.g._ R
packages, Ruby gems, etc, see @Ooms_2014] can easily be employed within a
Docker-based approach, allowing the operating-systems level virtualization
to sidestep potential issues such as external library dependencies or
conflicts with existing user libraries.  Other approaches that facilitate
reproducible research also introduce additional software dependencies
and possible points of failure [@FitzJohn_2014]. One example includes
dynamic documents [_e.g._ @Leisch_2002; @Peng_2011; @Xie_2013] which embed
the code required to re-generate the results within the manuscript.  As a
result, it is necessary to package the appropriate typesetting libaries
(_e.g._ \LaTeX) along with the code libaries such that the document executes
successfully for different researchers and platforms.

@@

<!-- These links don't appear in either pdf or rendered version, but provide some automatic linking on the Github rendering 
It would be nice if pandoc's reference syntax were closer to markdown's standard link syntax (e.g. always use [], bracket each reference)
-->
